---
output:
  reprex::reprex_document:
    venue: "gh"
    advertise: FALSE
    session_info: TRUE
    style: TRUE
    comment: "#;-)"
    tidyverse_quiet: FALSE
    std_out_err: TRUE
knit: reprex::reprex_render
---

This template demonstrates many of the bells and whistles of the `reprex::reprex_document()` output format. The YAML sets many options to non-default values, such as using `#;-)` as the comment in front of output.

## Code style

Since `style` is `TRUE`, this difficult-to-read code (look at the `.Rmd` source file) will be restyled according to the Tidyverse style guide when it's rendered. Whitespace rationing is not in effect!

```{r}
if(!require(multivar)) {
    install.packages("multivar")
    library(multivar)
}
if(!require(tidyverse)) {
    install.packages("tidyverse")
    library(tidyverse)
}
```

## MULTI-VAR:

STEP 1: Simulated data with time-series structure.

Here, we generate simulations for 9 different individuals, over 10 variables, with 100 times, which are gathered at regular intervals.

The following is a plot that shows the common structure across all simulated models.

```{r}

plot_sim(dat_multivar_sim, plot_type = "common")

```

Now, the plot below provides the time-series parameters for all 9 individuals. Through the plot, we can observe the common and individual structure

```{r}

plot_sim(dat_multivar_sim, plot_type = "total")

```


STEP 2: Construct a Multi-VAR model.

To create a multi-VAR model, we use the function `multivar::constructModel(data)`. Here, the `data` argument must be a $k$-list, where each element is a time series corresponding to each individual.

Here we explore the example of the object `dat_multivar_sim$data` loaded in the `"multivar"` package.

```{r}
class(dat_multivar_sim$data)
lapply(dat_multivar_sim$data, dim)


model <- multivar::constructModel(data = dat_multivar_sim$data)
class(model)

```

To fit, we perform cross-validation. This is done with the function `multivar::cv.multivar(model)`: 
```{r}

fit <- multivar::cv.multivar(model)

```

We can plot the result of the common structure with the function `plot_results(fit, plot_type = "common")`: 

```{r}

plot_results(fit, plot_type = "common")

```

We can go into further detail to visualize the individual models using the function `plot_results(fit, plot_type = "total")`:

```{r}

plot_results(fit, plot_type = "total")

```





## GIMME:

```{r}

install.packages("gimme")
library(gimme)

```

```{r}

data("simData", package = "gimme") 
# Run gimme with all the defaults 
outGIMME <- gimme(data = simData, )

plot(outGIMME)

```

